---
title: "Assignment 2"
format: html
editor: source
---


## Q3

a) Plotting the trends to show there is a point where the college and highschool earnings flip in terms of which is greater. 

```{r}
f_hs = function(x1, x2) {50 + 20*x1 + 0.07*x2 + 0.01*x1*x2}
f_college = function(x1, x2) {50 + 20*x1 + 0.07*x2 + 35 + 0.01*x1*x2 - 10*x1}

x1 = seq(0, 100, 1)
x2 = seq(0, 100, 1)

plot(x1, f_college(x1, x2), type = "l", col = "blue", xlim = c(0, 5), ylim = c(0, 250))
lines(x1, f_hs(x1, x2), type = "l", col = "red", xlim = c(0, 5), ylim = c(0, 250))
```

Notice highschool makes more only for x1 < 3.5 

## Q10

```{r}
library(ISLR2)
data(Carseats)
```

### (a)

```{r}
fit = lm(Sales ~ Price + Urban + US, data = Carseats)
summary(fit)
```

### (b)

For a one unit increase in price we see a 0.054 unit decrease in sales. 
For a store in an urban area we see a 0.02 unit increase in sales. 
For a store in the US we see a 1.2 unit increase in sales.

### (c)

The model in full equation form is the following: 

$$Price = 13.043 + 0.054*Price - 0.021*Urban + 1.2*US$$

### (d)

We can reject the null hypothesis for Price and US. 

### (e)

```{r}
fit2 = lm(Sales ~ Price + US, data = Carseats)
summary(fit2)
```

### (f)

We can see how well the models in (a) and (e) fit the data by looking at the R-squared values. The model in (a) has an R-squared value of 0.2397 and the model in (e) has an R-squared value of 0.2396. The model in (a) is slightly better at predicting the data.

```{r}
summary(fit)$r.squared
summary(fit2)$r.squared
```

### (g)

We can get the 95% CIs for the coefficients by using the confint() function. 

```{r}
confint(fit2, parm = c("(Intercept)", "Price", "USYes"), level = 0.95)
confint(fit, parm = c("(Intercept)", "Price", "USYes"), level = 0.95)
```

### (h)

To detect outliers in the model from (e) we can use the plot() function. 

```{r}
plot(fit2)
```
